The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-06 eswc-2012/workshop2.tex
point to footnotes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@154 43ef1190-90fd-4dd7-a769-d0121f02b80e

Mike Amundsen defines hypermedia types\footnote{\url{http://amundsen.com/hypermedia/}} as 
\begin{quote}
Hypermedia Types are MIME media types that contain native
hyper-linking semantics that induce application flow. For example,
HTML is a hypermedia type; XML is not.
\end{quote}
Furthermore, he defines a classification scheme called H~Factor as ``a
measurement of the level of hypermedia support and sophistication of a
media-type.'' The REST \& WOA Wiki defines ``the Hypermedia
Scale''\footnote{\url{http://restpatterns.org/Articles/The\_Hypermedia\_Scale}},
where the categorization is based on capabilities for create, read,
update and delete operations.  Considered on their own, RDF
serializations are hypermedia types, but only at the \textsf{LO} and
\textsf{CL} levels, and just an R~Type (read) on the Hypermedia
Scale. We aim at improving this situation.

>>>>

Mike Amundsen defines hypermedia types\footnote{\url{http://amundsen.com/hypermedia/}} as 
\begin{quote}
Hypermedia Types are MIME media types that contain native
hyper-linking semantics that induce application flow. For example,
HTML is a hypermedia type; XML is not.
\end{quote}
Furthermore, he defines a classification scheme called H~Factor as ``a
measurement of the level of hypermedia support and sophistication of a
media-type.'' The REST \& WOA Wiki defines ``the Hypermedia
Scale''\footnote{\url{http://restpatterns.org/Articles/The\_Hypermedia\_Scale}},
where the categorization is based on capabilities to do CRUD (Create,
Read, Update, Delete) operations.  Considered on their own, RDF
serializations are hypermedia types, but only at the \textsf{LO} and
\textsf{CL} levels (see footnotes for details), and just an R~Type
(read) on the Hypermedia Scale. We aim at improving this situation.
